EWJN from a BCS Superconductor

### 2021-02-02 paper.tex
Discussion from Meeting.

For a charge qubit with level separation $\omega$ and dipole moment $\vec{d}$, the relaxation rate $\frac{1}{T_1}$ depends on the qubit's distance from the surface $z$, as well as its orientation $i$.
The vacuum wavelength $\lambda = \frac{c}{\omega}$ is a natural unit for this distance $z$, so we wil measure $z$ in units of $\lambda$.
The electromagnetic field fluctuations that contribute to qubit relaxation have been described in~\cite{QubitRelax} and~\cite{Henkel1999}.
Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctations, and obtain the following expression:
\begin{equation}
	\frac{1}{T_1} = \frac{d^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E)}(z, \omega) \coth\frac{\omega}{2 T}.
\end{equation}
\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it.
Doesn't affect results so far, as \chi is unitless and only depends on quantities that are the same in SI / Gaussian.
Still bad though.}
Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.

>>>>

For a charge qubit with level separation $\omega$ and dipole moment $\vec{d}$, the relaxation rate $\frac{1}{T_1}$ depends on the qubit's distance from the surface $z$, as well as its orientation $i$.
The vacuum wavelength $\lambda = \frac{c}{\omega}$ is a natural unit for this distance $z$, so we wil measure $z$ in units of $\lambda$.
The electromagnetic field fluctuations that contribute to qubit relaxation have been described in~\cite{QubitRelax} and~\cite{Henkel1999}.
Both use Fermi's golden rule and the fluctuation-dissipation theorem to relate the relaxation rate to the spectral density of the field fluctuations, and obtain the following expression:
\begin{equation}
	\frac{1}{T_1} = \frac{d^2}{\epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{(E)}(z, \omega) \coth\frac{\omega}{2 T}.
\end{equation}
%\todo{All the Nam stuff is in Gaussian units, so should pick one unit system and stick with it. Doesn't %affect results so far, as $\chi$ is unitless and only depends on quantities that are the same in SI / %Gaussian. Still bad though.}
%Here and elsewhere we take $\hbar = k_{\mathrm{B}} = 1$.
